---
title: "R Notebook"
output: html_notebook
---

### Exercise 2.1

Use R to compute the product of the first 10 integers:\
1 \* 2 \* 3 \* 4 \* 5 \* 6 \* 7 \* 8 \* 9 \* 10

```{r}
print(1 * 2 * 3 * 4 * 5 * 6 * 7 * 8 * 9 * 10 )
```

### Exercise 2.2 Do the following using R:

1.  Compute the sum 924+124 and assign the result to a variable named a.
2.  Compute a\*a

```{r}
a <- 924+124
a * a
```

### Exercise 2.3 Answer the following questions:

What happens if you use an invalid character in a variable name? Try e.g., the following:

```{r}
# net income <- income - taxes
# net-income <- income - taxes
# ca$h <- income - taxes
```

What happens if you put R code as a comment? For example,

```{r}
income <- 100
taxes <- 20
net_income <- income - taxes
# gross_income <- net_income + taxes
```

What happens if you remove a line break and replace it by a semicolon ;? For example,

```{r}
income <- 200; taxes <- 30
```

What happens if you do two assignments on the same line? For example,

```{r}
income2 <- taxes2 <- 100
```

### Exercise 2.4 Do the following:

Create two vectors, height and weight, containing the heights and weights of five fictional people (i.e., just make up some numbers!).

Combine your two vectors into a data frame.

```{r}
height <- c(1.8, 1.7, 1.75, 1.77, 1.78) # meter (m)
weight <- c(80, 70, 67, 65, 66) # Kg
```

### Exercise 2.5

Try creating a vector using x \<- 1:5. What happens? What happens if you use 5:1 instead? How can you use this notation to create the vector\
(1,2,3,4,5,4,3,2,10)?

```{r}
x <- 1:5
print(x)
x <- 5:1 
print(x)
print(1:10)
```

### Exercise 2.6

Using the data you created in Exercise 2.4, do the following:

Compute the mean height of the people.

```{r}
mean(height)
```

Compute the correlation between height and weight.

```{r}
cor(height, weight)
```

### Exercise 2.7 Do the following:

Read the documentation for the function `length.` What does it do? Apply it to your `height` vector.

```{r}
?length
length(height)
```

Read the documentation for the function `sort`. What does it do? What does the argument `decreasing` (the values of which can be either `FALSE` or `TRUE`) do? Apply the function to your weight vector.

```{r}
?sort
sort(weight, decreasing = TRUE)
```

### Exercise 2.8 Compute the following:

1.  sqrt(pi)
2.  e\^2 \* (log(4))

```{r}
print(sqrt(pi))
print((exp(2))*(log(4)))
```

### Exercise 2.9

R will return non-numerical answers if you try to perform computations where the answer is infinite or undefined. Try the following to see some possible results:

Compute 1/0 Compute 0/0 Compute √−1

```{r}
print(1/0)
print(0/0)
print(sqrt(-1))
```

### Exercise 2.10

Install the palmerpenguins package from CRAN. We’ll use it for many of the exercises and examples that follow.

```{r}
install.packages("palmerpenguins")
```

```{r}
library(ggplot2)
```

### Exercise 2.11

Load the palmerpenguins package that you installed in Exercise 2.10, using `library(palmerpenguins)`. In this exercise, we’ll study the penguins dataset contained in said package. View the documentation for the penguins data and read about its variables. Check the data structures: how many observations and variables and what type of variables (numeric, categorical, etc.) are there?

```{r}
library(palmerpenguins)
View(penguins)
?penguins
str(penguins)
```

Compute summary statistics (means, median, min, max, counts for categorical variables). Are there any missing values?

```{r}
summary(penguins)
```
